Big data' og politologisk datavidenskab

### 2020-01-10 draft_v01.Rmd
first knit

---
title: "Big data & political science research"
subtitle: "Draft notes & outline"
output: word_document
---

>>>>

---
title: "'Big data' og politologisk datavidenskab"
author:
  - Frederik Hjorth
  - Matt W. Loftis
subtitle: "Udkast, januar 2020"
date:
  # "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  word_document: default
biblio-style: apsr
fontfamily: mathptmx
fontsize: 12pt
geometry: margin=1in
bibliography: references.bib
spacing: double
---
